Practical Machine Learning  
---  

author: "winnie"  

date: "Sunday, October 25, 2015"  

Overview  
---  
In this project, my goal will be to use data from accelerometers on the belt, forearm, arm, and dumbell of 6 participants. They were asked to perform barbell lifts correctly and incorrectly in 5 different ways. More information is available from the website [here](http://groupware.les.inf.puc-rio.br/har)  
The goal of your project is to predict the manner in which they did the exercise.  

Data Processing  
---  
```{r}
library(C50)
library(gmodels)
library(caret)
utils::View(training0)
training0 <- read.csv("pml-training.csv")
testing0 <- read.csv("Practical.csv")
prop.table(table(levels(training0$classe)))
```  
- library the packages that will be useful  
- make a propability table of the numbers of each acivity of the whole training set.  
- **We can see that the 5 manners are nearly uniformly distributed.  
```{r}
index <- grep("classe",names(training0))
index
```  
- Find out where the outcome variable is  

K-fold Cross Validation  and Sample Errors
---  

```{r}
nrow(training0)
w <- c()
for(i in 1:10){
w <- c(w,ifelse((nrow(training0)-2)%%i==0,T,F))
}
print(w)
k <- 5
(nrow(training0)-2)/5
w1 <- 1:3024
w2 <- 3025:7848
w3<- 7849:11772
w4<- 11773:15696
w5<- 15697:19622
```  
- Split the training set into less than 10 groups, make a loop to find out which k can be feasible. If w=TRUE then such number can be k. Here we can make k=5  
- w1 to w5 is the sequences to indicate where the test sets are, and the sets left behind will be train set.  
```{r}
set.seed(555)
training1 <- training0[order(runif(19622)),]
cvtest1 <- training1[w1,]
cvtrain1 <- training1[-w1,]
cvtest2 <- training1[w2,]
cvtrain2 <- training1[-w2,]
cvtest3 <- training1[w3,]
cvtrain3 <- training1[-w3,]
cvtest4 <- training1[w4,]
cvtrain4 <- training1[-w4,]
cvtest5 <- training1[w5,]
cvtrain5 <- training1[-w5,]
```  
- make 5 groups for cross validation, the training set should be randomly choosen from itself because the manners seems to distribute with some sort of orders.  
```{r}
model1 <- C5.0(cvtrain1[,1:159],cvtrain1$classe)
p1 <- predict(model1,cvtest1[,1:159],type="class")
confusionMatrix(p1,cvtest1[,160])

model2 <- C5.0(cvtrain2[,1:159],cvtrain2$classe)
p2 <- predict(model2,cvtest2[,1:159],type="class")
confusionMatrix(p2,cvtest2[,160])

model3 <- C5.0(cvtrain3[,1:159],cvtrain3$classe)
p3 <- predict(model3,cvtest3[,1:159],type="class")
confusionMatrix(p3,cvtest3[,160])

model4 <- C5.0(cvtrain4[,1:159],cvtrain4$classe)
p4 <- predict(model4,cvtest4[,1:159],type="class")
confusionMatrix(p4,cvtest4[,160])

model5 <- C5.0(cvtrain5[,1:159],cvtrain5$classe)
p5 <- predict(model5,cvtest5[,1:159],type="class")
confusionMatrix(p5,cvtest5[,160])

```  
- model1 to model5 are the tree predition models for k-fold cross validation, using the C5.0() from C50 package. C5.0 is a highly efficient method for tree predition.  
- p1 to p5 store the results of the preditions in model1 to model5  
- confusionMatrix() gives us Accuracy of the Cross Validation, model1 to model5 did a great job in prediting the result of test set with an average accuracy of 0.99+  

Apply the Model  and Get the Result
---  
```{r}
model <- C5.0(training1[,1:159],training1$classe)
pred <- predict(model,testing0[,1:159],type="class")
table(pred)
```  

- So make the tree model of the original training set and predict the manners in the test set which are A of all.



